\section{Kolmogorov extension theorem}
Assume \(X\) is a set and \((\mathcal{B}_n)_{n\in\mathbb{N}}\) is an increasing sequence of \(\sigma\)-algebras of subsets of \(X\). Assume \(\mu_n\) is a measure on \((X,\mathcal{B}_n)\) and 
\begin{align*}
    \mu_{n+1} \vert_{\mathcal{B}_n} = \mu_n \ \forall n.
\end{align*}
Can we define a measure \(\mu\) on \((X,\mathcal{B})\), where \(\mathcal{B}=\sigma\left(\cup_{n\in\mathbb{N}}\mathcal{B}_n\right)\) s.t. \(\mu\vert_{\mathcal{B}_n}=\mu_n \ \forall n\)? - In general, no. But we have the following:
\begin{theorem}[\ifcolor\color{red}\textbf{Kolmogorov extension theorem}\color{black}\else Kolmogorov extension theorem \fi]
    In the above settings, assume in addition that \(\mu_n(X)=1\ \forall n\) and there is a collection of subesets \(\mathcal{C}\subset\mathcal{B}\) s.t.:
    \begin{enumerate}[label=(\roman*)]
        \item \(\mu_n(A)=\sup\left\{ \mu_n(C): C\subset A, C\in\mathcal{C}\cap \mathcal{B}_n \right\}\) \(\forall A\in\mathcal{B}_n\);
        \item If \((C_n)_{n\in\mathbb{N}}\) is a sequence in \(\mathcal{C}\) and \(\cap_{n\in\mathbb{N}}C_n=\emptyset\), then \(\cap_{n=1}^{N}C_n=\emptyset\) for some \(N\). 
    \end{enumerate}
    Then there is a unique measure \(\mu\) on \((X,\mathcal{B})\) s.t. \(\mu\vert_{\mathcal{B}_n} = \mu\).
\end{theorem}

Assume now we have a collection \(((X_i,\mathscr{B}_i))_{i\in I}\) of measurable spaces (\(I\) can be infinite and uncountable). Consider \(X=\prod_{i\in I} X_i\). Denote by \(\prod_{i\in I}\mathscr{B}_i\) the \(\sigma\)-algebra generated by all sets of the form
\begin{align*}
    \prod\limits_{i\in F}A_i \times \prod\limits_{i\in F^c} X_j,
\end{align*}
where \(F\subset I\) is finite, \(A_i\in\mathscr{B}_i\) (\(i\in F\)).
\begin{example}
    Consider a sequence \(((X_n, d_n))_{n=1}^{\infty}\) of seperable metric spaces. Assume \(d_n(x,y)\leq 1\ \forall x,y\). (Any metric can be defined by such by defining \(\tilde{d}(x,y)=\frac{d(x,y)}{1 + d(x,y)}\).) Then \(\prod_{n=1}^{\infty}X_n\) is a metric space with metric
    \begin{align*}
        d(\underline{x}, \underline{y}) = \sum\limits_{n=1}^{\infty}\frac{1}{2^n}d_n(x_n,y_n),
    \end{align*}
    where \(\underline{x}=(x_n)_{n=1}^{\infty}\in X\). Given a sequence \((\underline{x}(n))_{n=1}^{\infty}\) in \(X\), we have \(\underline{x}(n)\xrightarrow[n\rightarrow\infty]{ }\underline{x}\) iff 
    \begin{align*}
        x(n)_k \xrightarrow[k\rightarrow\infty]{ } x_k \ \forall k.
    \end{align*}
    Consider the Borel \(\sigma\)-algebra \(\mathscr{B}(X_n)\). Then \(\prod_{n=1}^{\infty}\mathscr{B}(X_n)=\mathscr{B}(X)\). To see this, for every \(n\), choose open sets \(U_{n,k}\subset X_n\ (k=1,2,...)\) s.t. every open set in \(X_n\) is the union of some of \(U_{n,k}'\)s. This is possible by seperability: take a dense countable subset of \(X_n\) and then all balls of rational radii with centers at points of this subset. Then every open subset of \(X\) is the union of sets of the form
    \begin{align*}
        U_{1,k_1} \times U_{2,k_2}\times ...\times U_{n,k_n} \times \prod\limits_{m=n+1}^{\infty} X_m.
    \end{align*}
    Therefore such sets generate the \(\sigma\)-algebra \(\mathscr{B}(X)\), and as \(U_{n,k}\) \((k\in\mathbb{N})\) generate \(\mathscr{B}(X_n)\), we conclude that \(\prod_{n=1}^{\infty}\mathscr{B}(X_n)=\mathscr{B}(X)\).
\end{example}
In relation to this example, we will need the following:
\begin{theorem}[\colortheorem{Tikkonov, aso transcribed as Tychonoff}]
    Assume \(((X_n, d_n))_{n=1}^{\infty}\) is a sequence of compact metric spaces. Then \(\prod_{n=1}^{\infty}X_n\) (with metric as in the example) is compact.
\end{theorem}
\ifdetailed 
\begin{proof}
    \url{https://www.uio.no/studier/emner/matnat/math/MAT4400/v24/notater/lecture29.pdf}.
\end{proof}
\fi 
Return to a general collection \(((X_i,\mathscr{B}_i))_{i\in I}\) of measurable spaces. Let us introduce the following notation: For \(F\subset G\subset I\), write 
\begin{align*}
    &X_F = \prod\limits_{i\in F} X_i, \ X_G = \prod\limits_{i\in G} X_i, \\
    &\pi_{G,F}:X_G\rightarrow X_F \text{ for the projection map:}\\
    &\pi_{G,F}((x_i)_{i\in G}) = (x_i)_{i\in F},
\end{align*}
and recall the \colordefinition{pushforward measure}: given a measurable mapping \(f:X_1\rightarrow X_2\) and a measure \(\mu:\mathscr{B}\rightarrow [0,+\infty]\), the pushforward of \(\mu\) is the measure \(f_{*}(\mu):\mathscr{B}_2\rightarrow[0,+\infty] \) given by
\begin{align*}
    f_{*}(\mu)(B_2) = \mu\left(f^{-1}(B_2)\right) \text{ for } B_2\in\mathscr{B}_2.
\end{align*}
\begin{theorem}[\colortheorem{Kolmogorov extension theorem}]
    Assume \((X_i)_{i\in I}\) is a collection of metric spaces. Consider \(X=\prod_{i\in I}X_i\), \(\mathscr{B}=\prod_{i\in I}\mathscr{B}(X_i)\). Assume for every finite \(F\subset I\) we are given a regular Borel probability measure \(\mu_F\) on \(X_F\) s.t. 
    \begin{align*}
        (\pi_{G,F})_{*}\mu_G = \mu_F,
    \end{align*}
    for all finite \(F\subset G\subset I\). Then there is a unique probability measure \(\mu\) on \((X,\mathscr{B})\) s.t. 
    \begin{align*}
        (\pi_{I,F})_{*}\mu = \mu_F
    \end{align*}
    for all finite \(F\subset I\).
\end{theorem}
\begin{remark}
    If in addition the spaces \(X_i\) are seperable, then we can also conclude that for every \(A\in\mathscr{B}=\prod_{i\in I}\mathscr{B}(X_i)\) we have
    \begin{align*}
        \mu(A) = \sup\mu(C),
    \end{align*}
    where the supremum is taken over all sets \(C\subset A\) of the form 
    \begin{align*}
        C=K\times\prod\limits_{i\in I\backslash J} X_i,
    \end{align*}
    where \(J\subset I\) is countable and \(K\subset X_J\) is compact. 
\end{remark}